%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

    %------------------------------------------------

    \cventry
    {R\&D engineer - Working student} % Job title
    {ABB Robotics} % Organization
    {Munich, Germany} % Location
    {Nov. 2021 - PRESENT} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Development of internal tools.}
            \item {Maintaining the CMAKE build system.}
            \item {Maintaining Azure pipelines.}
        \end{cvitems}
    }

    %------------------------------------------------    

    \cventry
    {FPGA Engineer - Intern} % Job title
    {SmartRay} % Organization
    {Munich, Germany} % Location
    {Aug. 2021 - OCT. 2021} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Implementation of an Approximated FIR Filter on FPGA.}
            \item {Implementation of simulation software in Python.}
            \item {Creation of an automated build system using Python and Make.}
        \end{cvitems}
    }

    %------------------------------------------------    

    \cventry
    {Electrical Engineer - Working student} % Job title
    {NavVis} % Organization
    {Munich, Germany} % Location
    {Jan. 2021 - Jun. 2021} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Created a GPIO interface for linux devices using FTDI’s FT232H chip and PyFTDI.}
            \item {Supported the electrical engineering team by maintaining their codebase.}
            \item {Upgraded a tool to help the assembly team to test touch screens.}
            \item {Created a module that would parse the device’s hostnames using regex.}
            \item {Improved a test rig that is used to test LIDAR scanners for angular jumps and missing layers.}
            \item {Created a Python API to abstract FLIR\'s SDK for high speed cameras.}
            \item {Created a live viewer for the camera feed to test out cameras using the API in Python.}
        \end{cvitems}
    }

    %------------------------------------------------    

    \cventry
    {Undergrad research assistant} % Job title
    {United Arab Emirates University (UAEU)} % Organization
    {Al Ain, UAE} % Location
    {Jun. 2017 - Jun. 2020} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Created a digital controller and data acquisition system for a smart power grid.}
            \item {Programmed a traffic monitoring system using OpenCV and YOLO that achieved 95\% accuracy. (Paper)}
            \item {Created a neural network using TensorFlow for monthly water consumption prediction.}
            \item {Implementation of a bilateral filter using verilog.}
        \end{cvitems}
    }

    %------------------------------------------------    

    \cventry
    {Digital systems engineer - Intern} % Job title
    {National Space Science and Technology Center (NSSTC)} % Organization
    {Al Ain, UAE} % Location
    {May. 2019 - Sep. 2019} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item {Designed and synthesized a pseudo random number (PRN) generator for the SDR using Verilog.}
            \item {Created a simulation script to simulate the basic SDR functions and the modulator’s behavior.}
            \item {Set up a small GPS tracking device as a demonstration for a summer camp held by the center.}
            \item {Created internal documentation and guides for FreeRTOS.}
            \item {Setting up the CI/CD pipelines.}
        \end{cvitems}
    }

    %------------------------------------------------    



\end{cventries}